---
title: "Introducing {gs}"
output: 
  flexdashboard::flex_dashboard:
    navbar:
      - { title: "Learn more at the {gs} pkgdown site", 
          href: "https://jameslairdsmith.github.io/gs", 
          align: right }
---

<style type="text/css">

.sbframe-commentary{ 
      font-size: 20px;
}

.sourceCode{ 
      font-size: 18px;
}

pre code{ 
      font-size: 18px;
}

.storyboard-nav .sbframelist ul li {

  font-size: 20px;
}

.navbar-collapse {
  
  font-size: 18px;
}

.navbar-brand {
  
  font-size: 18px;
}

.my-title {

  font-size: 56px;
  text-align: center;
  font-weight: bold;
}

.my-subtitle {

  font-size: 40px;
  text-align: center;
}
.my-org {
  font-size: 40px;
  text-align: center;
  font-style: italic;
}
  
</style>

```{r setup, include=FALSE}
library(flexdashboard)
library(gs)
library(lubridate)
library(magrittr)

knitr::opts_chunk$set(eval=TRUE, include=TRUE, echo=TRUE)
```

```{r include=FALSE}
options(width=15)
```


About {gs}{.sidebar}
=====================================

### About {gs}

`gs` is a grammar of recurring calendar events, implemented as an R package. 
It enables users to easily create and work with schedules, even in cases when 
the pattern of events is irregular. 

`gs` does this by providing a set of simple to understand functions for making 
schedules along with functions for combining them to form more complex ones.

The `gs` grammar is both flexible and declarative. The flexibility allows users 
to compose arbitrarily complex schedules from simple and intuitive buildings 
blocks. Because the grammar is declarative, the user need not concern 
themselves with the details of how a particular schedule works, rather they 
can specify what they want from a schedule and let `gs` implement it for them.

### About me

My name is James Laird-Smith and I am a data analyst at the Financial Times in
London.

Home
=========================================

<div class = "my-title">
<br>
<br>
Introducing {gs}: <br>
A grammar of recurring calendar events
</div>
<div class = "my-subtitle">
<br>
James Laird-Smith <br>
<div class = "my-org">
The Financial Times (FT)
</div>
</div>

Simple examples {.storyboard}
=========================================

### Every 35 days {data-commentary-width=500}

```{r}
on_every_nth(35, "days", starting = dmy("28/01/2020")) %>% 
  schedule_days(during = 2020) 
```

***

To schedule days in increments from a certain date, we use the `on_every_nth()`
function. 

In this case we specify:

1. The number of increments between events is `35`
2. The type of increment is "days"
3. The start date is today.

### Friday the 13th {data-commentary-width=500}

```{r}
on_fri_thirteenth <- 
  on_wday("Fri") %>% 
  only_occur(on_mday(13))

on_fri_thirteenth %>% 
  schedule_days(from = 2020, to = 2022)
```

***

Friday the 13th can be thought of as the intersection of:

1. The schedule of all Fridays, found using the `on_wday()` function. 
2. The schedule of all 13th days of the month, using the `on_mday()` function.

The intersection of these two schedules is found by passing them as arguments
to the `also_occur()` function.


### The Monday of the 20th week of the year {data-commentary-width=500}

```{r}
### Assuming a week starts on Monday

in_isoweek_twenty <- in_isoweek(20)
on_mondays <- on_wday("Monday")

in_isoweek_twenty %>% 
  only_occur(on_mondays) %>% 
  schedule_days(from = 2020, to = 2025)
```

***

This schedule can be created as the intersection of two schedules:

1. The schedule of Mondays, created using the `on_wday()` function.
2. The schedule of events occurring in ISO week 20, created using the 
  `in_isoweek()` function.
  
The intersection of these schedules is found using the `only_occur()` function.


Advanced examples {.storyboard}
=========================================

### Every 12th Monday, Wednesday or Friday of the year {data-commentary-width=500}

```{r eval=TRUE, include=TRUE, echo=TRUE}
on_mon_wed_fri <- on_wday("Mon", "Wed", "Fri")

on_nth(12,
       on_mon_wed_fri, 
       within_given = "year") %>% 
  schedule_days(from = 2020, to = 2025)
```

***

This is a compound schedule with the following parts:

1. Days occurring on Monday, Wednesday or Friday. 
2. The 12th occurrence of an event within a period.

We can create the first schedule using the `on_wday()` function.

We can then use that schedule object as an argument to the `on_nth()`
function where we also specify that we want the 12th occurrence and that
it should be within each given year.

### Every 5th last Friday or Saturday of the month {data-commentary-width=500}

```{r}
on_fri_sat <- on_wday("Fri", "Sat")

on_nth(-5,
       on_fri_sat,
       within_given = "month") %>% 
  schedule_days(during = 2020)
```

***

Just like the previous example, this can be accomplished as a compound
schedule:

1. The first thing is to make the schedule of Fridays and Saturdays using the
   `on_wday()` function.
2. This schedule is then used as an argument to the `on_nth()` function where
   we also specify `-5` as the first argument.

The negative integer tells the `on_nth()` function to look for the *last* 
occurrence of the event within the particular period rather than the first.

### The first Saturday following the first Sunday of the month {data-commentary-width=500}

```{r}
on_first(on_wday("Sun"), within_given = "month") %>% 
  roll_forward(to_schedule = on_wday("Sat")) %>% 
  schedule_days(during = 2020)
```

***

There are two components to the schedule:

1. The first Sunday of the month, found using the `on_wday()` and `on_first()`
   functions.
2. The Saturday following the above schedule, found by rolling it forward using
   the `roll_forward()` function.

Holidays {.storyboard}
=========================================

### U.S. Independence Day {data-commentary-width=500}

```{r eval=TRUE, include=TRUE, echo=TRUE}
on_fourth_day_month <- on_mday(4)
in_july <- in_month("July")

on_us_independence_day <- 
  only_occur(on_fourth_day_month, 
             in_july)

on_us_independence_day %>% 
  schedule_days(from = 2020, to = 2025)
```

***

In the United States Independence Day is celebrated on **July 4th**, regardless
of the year.

This can be created as the intersection of two schedules:

1. The schedule of days occurring in July, found using the `in_month()` 
   function.
2. The schedule of all days occurring on the 4th of the month, found using the
   `on_mday()`.

The intersection of these schedules is found using the `only_occur()` function.

### Martin Luther King Jr. Day {data-commentary-width=500}

```{r eval=TRUE, include=TRUE, echo=TRUE}
on_mondays <- on_wday("Mon")
in_jan <- in_month("Jan")

on_mlk_day <- 
  on_third(on_mondays, 
           within_given = "month") %>% 
  only_occur(in_jan) 

on_mlk_day %>% 
  schedule_days(from = 2020, to = 2025)
```

***

Martin Luther King Jr. Day is a national holiday United States occurring every
year on the **third** **Monday** in **January**.

There are three parts to this schedule:

1. Events occurring on Mondays, created using `on_wday()`.
2. Events occurring in January, created using `in_month()`
3. The schedule of the nth event occurring in the period, in this case 
  `on_third()`.
  
The schedule of Mondays is passed into the `on_third()` function as an argument
along with the argument specifying it should be within a given month.

You can then get the desired schedule by finding the intersection of 
the above schedule with the schedule of January days using `only_occur()`.

### Combine holidays {data-commentary-width=500}

```{r eval=TRUE, include=TRUE, echo=TRUE}
on_us_federal_holidays <-
  on_us_independence_day %>% 
  also_occur(on_mlk_day)

on_us_federal_holidays %>% 
  schedule_days(from = 2020, to = 2022)
```

*** 

If you want to create a schedule of multiple holidays, you can compose it using
individual schedule objects of those holidays.

In this example, we take the schedule objects we have already created for
US Independence Day and Martin Luther King Jr. Day and combine them using the
`also_occur()` function.

This can be done any number of times to create a schedule that is arbitrarily
complex.
